% Autogenerated translation of README.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\setmainfont{Helvetica Neue}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}

\chapter*{T490-Hackintosh-Opencore}

This is Opencore for Thinkpad T490.
OC Version 0.8.3

\chapter*{File included.}

\begin{itemize}
\item ACPI

\begin{itemize}
\item BlockOptane.aml
\item SSDT-AWAC.aml
\item SSDT-EC-USBX-LAPTOP.aml
\item SSDT-PLUG-DRTNIA.aml
\item SSDT-PNLF.aml
\item SSDT-RHUB.aml
\end{itemize}
\item Kexts

\begin{itemize}
\item AirportItlwm.kext
\item AppleALC.kext
\item BrightnessKeys.kext
\item ECEnabler.kext
\item IntelBluetoothFirmware.kext
\item IntelBluetoothInjector.kext
\item IntelMausi.kext
\item Lilu.kext
\item NVMeFix.kext
\item SMCBatteryManager.kext
\item SMCLightSensor.kext
\item SMCProcessor.kext
\item SMCSuperIO.kext
\item USBToolBox.kext
\item UTBMap.kext
\item VirtualSMC.kext
\item VoodooPS2Controller.kext
\item WhateverGreen.kext
\end{itemize}
\item Drivers

\begin{itemize}
\item HfsPlus.efi
\item OpenCanopy.efi
\item OpenRuntime.efi \\
\end{itemize}
\item Tools

\begin{itemize}
\item OpenShell.efi 
\end{itemize}
\end{itemize}

\chapter*{Compability}

\begin{itemize}
\item Optane SSD support. For modle 20RY.
\item macOS 11.6 tested. However macOS 13 may work.
\item Intel bluetooth and wlan. The airplay will display but it does not work.
\item Hand Off is suppoorted.
\item Light sensor OK.
\item Camera OK.
\item tracepad OK.
\item Sleep function ok.
\end{itemize}

\chapter*{How to use?}

\begin{enumerate}
\item Clone this repo.
\item Modify SMBIOS info.
\item Compile \texttt{BlockOptane.dsl} if you are using optane.
\end{enumerate}

\chapter*{Information for Optane}

Please refer to this \href{https://github.com/dortania/OpenCore-Install-Guide/pull/388}{PR \#388}

\end{document}
